\documentclass{article}

\usepackage{natbib}
\usepackage{booktabs}
\usepackage{amsmath,amsthm}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{longtable}

\hypersetup{
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with
%linkbordercolor)
citecolor=blue,       % color of links to bibliography
filecolor=magenta,   % color of file links
urlcolor=cyan           % color of external links
}

\title{Ao's Notes on Medical Imaging Software}

\author{Ao Dong}

\date{\today}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Author(s)} & \textbf{Change}\\
\midrule
Jan/30/2020 & Ao Dong & Initial draft\\
Feb/02/2020 & Ao Dong & Update\\
Feb/08/2020 & Ao Dong & Changed table to a spreadsheet link\\
\bottomrule
\end{tabularx}
\end{table}

\section{Software List}

The link to the software list (Google Sheet): \href{https://docs.google.com/spreadsheets/d/122wU0v3ZtvDcqy8C4zKJ89kU-8fXAbo3Mzn6vcVXOi0/edit?usp=sharing}{LINK}

\noindent There are 50 packages in the list.

\subsection{Sources}

The above list is built based on 7 sources - 3 academical papers, 3 blog articles, and 1 online forum discussion. All of the sources are recorded on the second sheet in the list.

\subsection{Orders}

The software packages are put in the list roughly by the order of how many times they are mentioned in the above sources.

\subsection{Selection}

A few software packages mentioned in the sources are excluded, since they are in the following cases:
\begin{itemize}
    \item Commercialized. Some software are not free any more. For example, PacsOne Premium, JVS-DiComPlus, RadiAnt, Synedra, TurtleSeg, AlgoM, Athena.
    \item No recent updates. A few software without recent release are excluded, such as PacsOne Basic (2005), K-PACS (developed for Windows XP or Windows VISTA), JVS-DiCom (2012), MITO-DICOM Viewer (2015), Aeskulap (2007), Fusionviewer (2008), Kradview (2013), Mayam (2013), Eviewbox (2015), EzDICOM (2013), Agnosco (2011), ONIS Free Version (2016 and not open-source), DICOMscope (2001).
\end{itemize}

\subsection{Categories}

The software packages are roughly divided into 3 major categories - Tool Kit, PACS, and Viewer.
\begin{itemize}
    \item Tool Kits are usually used by developers to create new software, and there are only a few of them in the list. 
    \item PACS stands for Picture Archiving and Communications System, which can be regarded as a type of server. There are also only several of them in the list, since most PACS solutions are commercial nowadays.
    \item  Most software in the list are in the Viewer category, and many of these ones also provide other functions such as analysis, conversion, segmentation, etc.
\end{itemize}

\section{Quality Measurements}

\subsection{Interoperability}
There are not many measuring methods in papers, and most of them are very
complicated.
\begin{itemize}
\item Can the workstation software (for visualization, analysis, etc.) connect
with the PACS (server)?
    \item Does the software use output from or provide input to other software?
    \item Can the software work with customized plug-ins? 
\end{itemize}

\noindent Measuring aspects from \citep{SmithEtAl2018}:
\begin{itemize}
    \item Does the software interoperate with external systems? ({yes*, no})
    \item Is there a workflow that uses other softwares? ({yes*, no})
\item If there are external interactions, is the API clearly defined? ({yes*,
no, n/a})
\end{itemize}

\subsection{Visibility/Transparency}
\begin{itemize}
\item Does the software use any version and issue tracking system, such as
Github, Gitlab for development?
\item Does the software have documents recording the development process and
status?
\item Does the software have clear release log with essential information, such
as release date, bug fixed and new features?
\end{itemize}

\noindent Measuring aspects from \citep{SmithEtAl2018}:
\begin{itemize}
\item Is the development process defined? If yes, what process is used. ({yes*,
no, n/a})
\item Ease of external examination relative to other products considered? ({1 ..
10})
\end{itemize}

\subsection{Productivity}
Can be measured by the summation of all output (such as the number of lines of
new code, the number of pages of new documents and the number of new test cases)
produced per person-day.

However, it is hard for a third party to carry out the above method without
knowing the exact number of developers or how much time they spent on the
project.

\subsection{Completeness}

\subsection{Consistency}

\newpage

\bibliographystyle {plainnat}
\bibliography {../CommonFiles/ResearchProposal}

\end{document}