\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{xspace}
\usepackage{fullpage}
\usepackage{hyperref}

\hypersetup{
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with
%linkbordercolor)
citecolor=blue,       % color of links to bibliography
filecolor=magenta,   % color of file links
urlcolor=cyan           % color of external links
}

%% Comments
\newif\ifcomments\commentstrue

\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi

\newcommand{\wss}[1]{\authornote{blue}{SS}{#1}} %Spencer Smith
\newcommand{\jc}[1]{\authornote{red}{JC}{#1}} %Jacques Carette
\newcommand{\oo}[1]{\authornote{magenta}{OO}{#1}} %Olu Owojaiye
\newcommand{\pmi}[1]{\authornote{green}{PM}{#1}} %Peter Michalski
\newcommand{\ad}[1]{\authornote{cyan}{AD}{#1}} %Ao Dong

\title{Questionnaire to Developers} 
\author{Ao Dong}
\date{\today}

\begin{document}

\maketitle
Several questions are borrowed from \href{https://gitlab.cas.mcmaster.ca/smiths/pub/-/blob/master/Jegatheesan2016.pdf}{Jegatheesan2016}

\section{Information about the developers and users}
\begin{enumerate}
\item Interviewees' current position/title? degrees?
\item Interviewees' contribution to/relationship with the software?
\item Length of time the interviewee has been involved with this software?
\item How large is the development group?
\item What is the typical background of a developer?
\item How large is the user group?
\item What is the typical background of a user?
\end{enumerate}

\section{Information about the software}

\begin{enumerate}
\item \ad{General} What is the most important software quality(ies) to your work? (set of selected qualities plus "else")
\item \ad{General} Are there any examples where the documentation helped? If yes, how it helped. ({yes$^*$, no})
\item \ad{General} Is there any documentation you feel you should produce and do not? If yes, what is it and why? ({yes$^*$, no})
\item \ad{Completeness} Do you address any of your quality concerns using documentation? If yes, what are the qualities and the documents. ({yes$^*$, no})
\item \ad{Visibility/Transparency} Is there a certain type of development methodologies used during the development? (\{Waterfall, Scrum, Kanban, else\})
\item \ad{Visibility/Transparency} Is there a clearly defined development process? If yes, what is it. (\{yes$^*$, no\})
\item \ad{Visibility/Transparency} Are there any project management tools used during the development? If yes, what are they. (\{yes$^*$, no\})
\item \ad{Visibility/Transparency} Going forward, will your approach to documentation of requirements and design
change? If not, why not. (\{yes, no$^*$\})
\item \ad{Correctness and Verifiability} During the process of development, what tools or techniques are used to build confidence of correctness? (string)
\item \ad{Correctness and Verifiability} Do you use any tools to support testing? If yes, what are they. (e.g. unit testing tools, regression testing suites) (\{yes$^*$, no\})
\item \ad{Correctness and Verifiability} Is there any document about the requirements specifications of the program? If yes, what is it. (\{yes$^*$, no\})
\item \ad{Portability} Do you think that portability has been achieved? If yes, how? (\{yes$^*$, no\})
\item \ad{Maintainability} How was maintainability considered in the design? (string)
\item \ad{Maintainability} What is the maintenance type? (set of \{corrective, adaptive, perfective,
unclear\})
\item \ad{Reusability} How was reusability considered in the design? (string)
\item \ad{Reusability} Are any portions of the software used by another package? If yes, how they are used. ({yes$^*$, no})
\item \ad{Reproducibility} Is reproducibility important to you? ({yes$^*$, no})
\item \ad{Reproducibility} Do you use tools to help reproduce previous software results? If yes, what are they. (e.g. version control, configuration management) ({yes$^*$, no})
\item \ad{Completeness} Is any of the following documents used during the development? ({yes$^*$, no})
\item \ad{General} Will this experience influence how you develop software? Do you see yourself maintaining the same level of documentation, tool support as you go forward? (string)
\begin{itemize}
\item Module Guide
\item Module Interface Specification
\item Verification and Validation Plan
\item Verification and Validation Report
\end{itemize}
\end{enumerate}

\end{document}