\documentclass[12pt]{article}

\usepackage{natbib}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage[normalem]{ulem}

\hypersetup{
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with
%linkbordercolor)
citecolor=blue,       % color of links to bibliography
filecolor=magenta,   % color of file links
urlcolor=cyan           % color of external links
}

%% Comments
\newif\ifcomments\commentstrue

\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi

\newcommand{\wss}[1]{\authornote{blue}{SS}{#1}} %Spencer Smith
\newcommand{\jc}[1]{\authornote{red}{JC}{#1}} %Jacques Carette
\newcommand{\oo}[1]{\authornote{magenta}{OO}{#1}} %Olu Owojaiye
\newcommand{\pmi}[1]{\authornote{green}{PM}{#1}} %Peter Michalski
\newcommand{\ad}[1]{\authornote{brown}{AD}{#1}} %Ao Dong

\title{Questions to Developers} 
\author{Ao Dong}
\date{\today}

\begin{document}

\maketitle
\pmi{A pilot will be conducted with these questions to test them. Test subjects may include PhD students.}
\section{Information about the developers and users}\citep{Jegatheesan2016}
\begin{enumerate}
\item Interviewees' current position/title? degrees?
\item Interviewees' contribution to/relationship with the software?
\item Length of time the interviewee has been involved with this software?
\item How large is the development group?
\item Do you have a defined process for accepting new contributions into your team?
\item What is the typical background of a developer?
\item What is your estimated number of users? How did you come up with that estimate?
\item What is the typical background of a user?
\end{enumerate}

\section{Information about the software}

\noindent\ad{3 aspects: dev process, software quality, user feedback}

\pmi{consider adding `What, if any, actions were taken to address x?' to most/all questions, similar to question 10}

Square brackets are used for traceability to qualities and relevant research questions found in the  \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Methodology.pdf}{methodology document}. 

\begin{enumerate}
\item Currently, what are the most significant obstacles in your development
process?
\item How might you change your development process to remove or reduce these
obstacles?
\item How does documentation fit into your development process? Would improved
documentation help with the obstacles you typically face? [traceability - research question 5b, visibility/transparency - research question 5i]
\item In the past, is there any major obstacle to your development process that
has been solved? How did you solve it?
\item What is your software development model? For example, waterfall, agile, etc.
\item What is your project management process? Do you think improve this process
can tackle the current problem? Were any project management tools used?
\item \sout{Can you name several software qualities that are the most important to
this project?}
\item Was it hard to ensure the correctness of the software? If there were any
 obstacles, what methods have been considered or practiced to improve the situation? If practiced, did it work? [correctness - research question 5e]
\item When designing the software, did you consider the ease of future changes?
 For example, will it be hard to change the structure of the system, modules or code blocks? What measures have been taken to ensure the ease of future changes and maintains? [maintainability - research question 5d, modifiability - research question 5c]
\item Provide instances where users have misunderstood the software. What, if any, actions were taken to address understandability issues? [understandability - research question 5f]
\item What, if any, actions were taken to address usability issues? [usability - research question 5a]
\item Do you think the current documentation can clearly convey all necessary
knowledge to the users? If yes, how did you successfully achieve it? If no, what
improvements are needed? [unambiguity - research question 5g]
\item Do you have any concern that your computational results won't be
reproducible in the future? Have you taken any steps to ensure reproducibility? [reproducibility - research question 5h]
\end{enumerate}


\subsection{Old notes from methodology: Information about the software}
Compare to questions above and then delete this subsection

\begin{enumerate}
	\item \ad{General} What is the most important software quality(ies) to your
	work? (set of selected qualities plus "else")
	\item \ad{General} Are there any examples where the documentation helped? If
	yes, how it helped. ({yes$^*$, no})
	\item \ad{General} Is there any documentation you feel you should produce and do
	not? If yes, what is it and why? ({yes$^*$, no})
	\item \ad{Completeness} Do you address any of your quality concerns using
	documentation? If yes, what are the qualities and the documents. ({yes$^*$,
		no})
	\item \ad{Visibility/Transparency} Is there a certain type of development
	methodologies used during the development? (\{Waterfall, Scrum, Kanban,
	else\})
	\item \ad{Visibility/Transparency} Is there a clearly defined development
	process? If yes, what is it. (\{yes$^*$, no\})
	\item \ad{Visibility/Transparency} Are there any project management tools used
	during the development? If yes, what are they. (\{yes$^*$, no\})
	\item \ad{Visibility/Transparency} Going forward, will your approach to
	documentation of requirements and design change? If not, why not. (\{yes,
	no$^*$\})
	\item \ad{Correctness and Verifiability} During the process of development, what
	tools or techniques are used to build confidence of correctness? (string)
	\item \ad{Correctness and Verifiability} Do you use any tools to support
	testing? If yes, what are they. (e.g. unit testing tools, regression testing
	suites) (\{yes$^*$, no\})
	\item \ad{Correctness and Verifiability} Is there any document about the
	requirements specifications of the program? If yes, what is it. (\{yes$^*$,
	no\})
	\item \ad{Portability} Do you think that portability has been achieved? If yes,
	how? (\{yes$^*$, no\})
	\item \ad{Maintainability} How was maintainability considered in the design?
	(string)
	\item \ad{Maintainability} What is the maintenance type? (set of \{corrective,
	adaptive, perfective, unclear\})
	\item \ad{Reusability} How was reusability considered in the design? (string)
	\item \ad{Reusability} Are any portions of the software used by another package?
	If yes, how they are used. ({yes$^*$, no})
	\item \ad{Reproducibility} Is reproducibility important to you? ({yes$^*$, no})
	\item \ad{Reproducibility} Do you use tools to help reproduce previous software
	results? If yes, what are they. (e.g. version control, configuration
	management) ({yes$^*$, no})
	\item \ad{Completeness} Is any of the following documents used during the
	development? ({yes$^*$, no})
	\item \ad{General} Will this experience influence how you develop software? Do
	you see yourself maintaining the same level of documentation, tool support as
	you go forward? (string)
	\begin{itemize}
		\item Module Guide
		\item Module Interface Specification
		\item Verification and Validation Plan
		\item Verification and Validation Report
	\end{itemize}
\end{enumerate}

\newpage

\bibliographystyle {plainnat}
\bibliography {../../CommonFiles/ResearchProposal}

\end{document}